Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-02 paper/paper.tex
done V.0 and V.A

project. It includes real network traffic of a busy private network
access point to the Internet. We also used data sets from the
Stratosphere IPS Project~\cite{stratosphere-normal} including, for
example, the regular traffic of a university network.
\noindent\textbf{Ground Truth.}~To objectively evaluate \tname{}'s performance we
compared the rules it generates with \emph{trusted rules}. We used
the ``Emerging Threats Open Ruleset''~\cite{emerging-threats-open} for
that. After finding a matching pair of attack and corresponding rule
using the procedure described in
Section~\ref{subsec:malicious-traffic}, we reproduced the attack to
confirm the rule captures the attack in isolation (and no noise was
introduced in the process). Column ``Ground Truth'' from
Table~\ref{table:attacks} only shows the essential
options. Documentation options (\eg{}, ``msg'') are discarded.

>>>>

project. It includes real network traffic of a private network. We
also used data sets from the Stratosphere IPS
Project~\cite{stratosphere-normal} including, for example, the regular
traffic of a university network.
\noindent\textbf{Ground Truth.}~To objectively evaluate \tname{}'s
performance we compared the rules it generates with \emph{trusted
  rules}. We used the ``Emerging Threats Open
Ruleset''~\cite{emerging-threats-open} for that. After finding a
matching pair of attack and corresponding rule using the procedure
described in Section~\ref{subsec:malicious-traffic}, we reproduced the
attack to confirm the rule captures the attack in isolation. Column
``Ground Truth'' from Table~\ref{table:attacks} only shows the
essential options. Documentation options (\eg{}, ``msg'') are
discarded.
